Pillar 2 - (STM) Topic Modeling

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
clean workspace

```{r} 
#testing 
test_model <- stm_eval_model[1, ]

my_stm_eval(list(test_model$documents, test_model$vocab, test_model$n_topic))

my_stm_eval(documents = test_model$documents, vocab = test_model$vocab, n_topic = test_model$n_topic)

test <- list(test_model$documents, test_model$vocab, test_model$n_topic)
test %>% my_stm_eval

test <- list(stm_eval_model$documents, stm_eval_model$vocab, stm_eval_model$n_topic)

test %>% my_stm_eval

test <- stm_eval_model %>% mutate(test = list(documents, vocab, n_topic) %>% pmap(list))

stm_eval_model %>% mutate(test = test %>% map(my_stm_eval))
test1<- test$test[[1]]

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```

>>>>

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
```

```{r clean workspace}
#clean workspace
rm(# Generating functions:
  my_stm, my_stm_eval,
  #Extraction Functions
  extract_dtm, extract_corpus, extract_documents, extract_vocab, extract_data,
  extract_held_doc, extract_held_vocab, extract_helout_missing, 
  my_model, my_tidy_gamma,
  get_top_terms_topic, 
  get_top_topics_course,
  get_kw
  )
```
